Load Shifting Versus Manual Frequency Reserve: \\ Which One is More Appealing to Flexible Loads?

### 2024-01-05 tex/figures/timeline_mfrr_variables_tikz.tex
Preparing for submission to new journal.

  \draw[rounded corners, fill=RectangleColor, very thick] (0, 1) rectangle (4, 3) node[midway]{\LARGE mFRR \\ \LARGE reservation};
  \node at (2,0) {\LARGE $\lambda_{h}^{\rm{r}} p_{h}^{\rm{r},\uparrow}$};
  \node at (2,-2) {\LARGE D$-$1};
  \node at (2,-2.7) {\large (9:30am)};

  \draw[rounded corners, fill=RectangleColor, very thick] (5, 1) rectangle (9, 3) node[midway]{\LARGE Day-ahead \\ \LARGE cost};
  \node at (7,0) {\LARGE $-\lambda_{h}^{\rm{s}} p_{h}^{\text{Base}}$};
  \node at (7,-2) {\LARGE D$-$1};
  \node at (7,-2.7) {\large (12:00pm)};

  \draw[rounded corners, fill=RectangleColor, very thick] (10, 1) rectangle (14, 3) node[midway]{\LARGE Regulating \\ \LARGE power bid};
  \node at (12,0) {\LARGE $\lambda_{h}^{\text{bid}}$};
  \node at (12,-2) {\LARGE D$-$1};
  \node at (12,-2.7) {\large (5:00pm)};

  \draw[name path=VerticalDashedLine, dashed, line width=0.45mm, black](14.5,-1)--(14.5,3);

  \draw[rounded corners, fill=RectangleColor, very thick] (15, 1) rectangle (19, 3) node[midway]{\LARGE mFRR \\ \LARGE activation};
  \node at (17,0) {\LARGE $\lambda_{h}^{\rm{b}} p_{h}^{\rm{b},\uparrow}$};
  \node at (17,-2) {\LARGE D};
  \node at (17,-2.7) {\large (12pm -- 12am)};

  \draw[rounded corners, fill=RectangleColor, very thick] (20, 1) rectangle (24, 3) node[midway]{\LARGE Rebound \\ \LARGE cost};
  \node at (22,0) {\LARGE $-\lambda_{h}^{\rm{b}} p_{h}^{\rm{b},\downarrow}$};
  \node at (22,-2) {\LARGE D};
  \node at (22,-2.7) {\large (12pm -- 12am)};

>>>>

  \draw[rounded corners, fill=RectangleColor, very thick] (0, 1) rectangle (4, 3) node[midway]{\LARGE mFRR \\ \LARGE reservation};
  \node at (2,0) {\LARGE  $p_{h}^{\rm{r},\uparrow}$};
  \node at (2,-2) {\LARGE D$-$1};
  \node at (2,-2.7) {\large (9:30am)};

  \draw[rounded corners, fill=RectangleColor, very thick] (5, 1) rectangle (9, 3) node[midway]{\LARGE Day-ahead \\ \LARGE clearing};
  \node at (7,-2) {\LARGE D$-$1};
  \node at (7,-2.7) {\large (12:00pm)};

  \draw[rounded corners, fill=RectangleColor, very thick] (10, 1) rectangle (14, 3) node[midway]{\LARGE Regulating  \\ \LARGE power bid};
  \node at (12,0) { \LARGE $\lambda_{h,\omega}^{\text{bid}}$};
  \node at (12,-2) {\LARGE D$-$1};
  \node at (12,-2.7) {\large (5:00pm)};

  \draw[rounded corners, fill=RectangleColor, very thick] (15, 1) rectangle (19, 3) node[midway]{\LARGE Real time};
  \node at (17,0) {\LARGE $\Gamma_{h,\omega}$};
  % {\LARGE $\Bigl( \bm{p}^{\rm{r},\uparrow}, \bm{\lambda}_{\omega}^{\text{bid}}, \bm{p}_{\omega}^{b,\uparrow}, \bm{p}_{\omega}^{b,\downarrow}, \bm{s}_{\omega}, \bm{T}_{\omega}^{c}, \bm{T}_{\omega}^{f}, \notag \\ \quad & \quad \bm{T}_{\omega}^{c, B}, \bm{T}_{\omega}^{f,B}, \bm{\phi}_{\omega}, \bm{g}_{\omega} \Bigr)$};
  \node at (17,-2) {\LARGE D};
  \node at (17,-2.7) {\large (12pm -- 12am)};
